---
title: "hw2-Q2"
author: "Yiyi Xu"
date: "9/13/2018"
output:
  word_document: default
  html_document: default
---

```{r}
options(digits=20)
```
## .Machine$double.eps

.Maitchine$double.eps is the smallest positive floating- point number as it equals to 2^(-52) 
```{r }
.Machine$double.eps
1+  .Machine$double.eps==1
1-  .Machine$double.eps==1
.Machine$double.base ^ (.Machine$double.ulp.digits) == .Machine$double.eps
```

## .Machine$double.neg.eps

.Machine$double.neg.eps is a small positive floating-point number which equals to 2^(-52-1L).Also, it is the smallest positive number such that 1+x==1
```{r}
.Machine$double.neg.eps
 .Machine$double.base ^ (.Machine$double.ulp.digits - 1L)==.Machine$double.neg.eps
1- .Machine$double.neg.eps==1
1+ .Machine$double.neg.eps==1
1+ .Machine$double.base ^ (.Machine$double.ulp.digits - 2L)==1
1+ .Machine$double.base ^ (.Machine$double.ulp.digits - 3L)==1

```

## .Machine$double.xmax

.Machine$double.xmax is a large normalized floating-point number, but not the largest number in my machines. In some machines, it may be the largest number.
```{r}
.Machine$double.xmax
(1 - .Machine$double.neg.eps) * .Machine$double.base ^ .Machine$double.max.exp
(1 - .Machine$double.neg.eps) * .Machine$double.base ^ .Machine$double.max.exp ==.Machine$double.xmax
```

## .Machine$double.xmin

.Machine$double.xmin is the smallest postive normalized floating-point number equals 2^(-1022)
```{r}
.Machine$double.xmin
.Machine$double.base ^ (.Machine$double.min.exp)
.Machine$double.base ^ (.Machine$double.min.exp) == .Machine$double.xmin
```
